Towards a Cognitive System That Can Recognize Spatial Regions Based on Context

### 2012-01-25 code/scenarios/cdsr/trunk/papers/AAAI2012/main-aaai12-cdsr.tex
minor edits page 2 and fig 4

Dora's metric map is a collection of lines in a 2D global coordinate frame. These lines are generated by a process which uses input from the robot's odometry and laser scanner to perform simultaneous localization and mapping (SLAM). Lines in this SLAM map represent features extracted from laser scans wherever a straight line is present for long enough to be considered permanent. In practice, lines are generated at the positions of walls and any other objects that are flat at the height of the laser (e.g. bins, closed doors etc.). The robot's location in the metric layer is represented as a 2D position plus an orientation.

@@

\begin{figure}
	% can swap these 2 lines for different presentations - and colours!
 \includegraphics[width=\columnwidth]{images/worked-example.png}
  % \includegraphics[width=\columnwidth]{images/worked-example-rooms.png}
  \caption{Maps of 2 real classrooms generated by our system, plus an expert-annotated CDSR (red, top image), subject-annotated CDSR (blue, bottom image) and a (smaller) CDSR transferred by analogy (green bottom image). The classroom used to generate the bottom classroom is pictured in Figure~\ref{fig:ug40}.}
  \label{fig:rooms}
\end{figure}

>>>>

Dora's metric map is a collection of lines in a 2D global coordinate frame. Two example maps are pictured in Figure~\ref{fig:rooms}. These lines are generated by a process which uses input from the robot's odometry and laser scanner to perform simultaneous localization and mapping (SLAM). Lines in this SLAM map represent features extracted from laser scans wherever a straight line is present for long enough to be considered permanent. In practice, lines are generated at the positions of walls and any other objects that are flat at the height of the laser (e.g. bins, closed doors etc.). The robot's location in the metric layer is represented as a 2D position plus an orientation.

@@

\begin{figure}
	% can swap these 2 lines for different presentations - and colours!
 \includegraphics[width=\columnwidth]{images/worked-example.png}
  % \includegraphics[width=\columnwidth]{images/worked-example-rooms.png}
  \caption{Maps of 2 real classrooms generated by our system. The lines around the perimeter are walls, the unfilled polygons are the outlines of objects and the filled polygons are CDSRs. The maps show an expert-annotated CDSR (red, top image), a subject-annotated CDSR (blue, bottom image) and a CDSR transferred by analogy (green bottom image). The classroom used to generate the bottom classroom is pictured in Figure~\ref{fig:ug40}.}
  \label{fig:rooms}
\end{figure}
